\section{2004}
Hunting for a job late last year, lawyer Gant Redmon stumbled across CareerBuilder, a job database on the Internet. He searched it with no success but was attracted by the site’s “personal search agent.” It’s an interactive feature that lets visitors key in job criteria such as location, title, and salary, then E-mails them when a matching position is posted in the database. Redmon chose the keywords legal, intellectual property, and Washington, D.C. Three weeks later, he got his first notification of an opening. “I struck gold,” says Redmon, who E-mailed his resume to the employer and won a position as in-house counsel for a company.
With thousands of career-related sites on the Internet, finding promising openings can be time-consuming and inefficient. Search agents reduce the need for repeated visits to the databases. But although a search agent worked for Redmon, career experts see drawbacks. Narrowing your criteria, for example, may work against you: “Every time you answer a question you eliminate a possibility,” says one expert.
For any job search, you should start with a narrow concept -- what you think you want to do -- then broaden it. “None of these programs do that,” says another expert. “There’s no career counseling implicit in all of this.” Instead, the best strategy is to use the agent as a kind of tip service to keep abreast of jobs in a particular database; when you get E-mail, consider it a reminder to check the database again. “I would not rely on agents for finding everything that is added to a database that might interest me,” says the author of a job-searching guide.
Some sites design their agents to tempt job hunters to return. When CareerSite’s agent sends out messages to those who have signed up for its service, for example, it includes only three potential jobs -- those it considers the best matches. There may be more matches in the database; job hunters will have to visit the site again to find them -- and they do. “On the day after we send our messages, we see a sharp increase in our traffic,” says Seth Peets, vice president of marketing for CareerSite.
Even those who aren’t hunting for jobs may find search agents worthwhile. Some use them to keep a close watch on the demand for their line of work or gather information on compensation to arm themselves when negotiating for a raise. Although happily employed, Redmon maintains his agent at CareerBuilder. “You always keep your eyes open,” he says. Working with a personal search agent means having another set of eyes looking out for you.
\begin{questions} \sethlcolor{cyan} \question 41.	How did Redmon find his job?\\
\fourch{ By searching openings in a job database.
}{ By posting a matching position in a database.
}{ By using a special service of a database.
}{ By E-mailing his resume to a database.
} \question 42.	Which of the following can be a disadvantage of search agents?\\
\fourch{ Lack of counseling.
}{ Limited number of visits.
}{ Lower efficiency.
}{ Fewer successful matches.
} \question 43.	The expression “tip service” (Line 4, Paragraph 3) most probably means \ltk{}.\\
\fourch{ advisory
}{ compensation
}{ interaction
}{ reminder
} \question 44.	Why does CareerSite’s agent offer each job hunter only three job options?\\
\twoch{ To focus on better job matches.
}{ To attract more returning visits.
}{ To reserve space for more messages.
}{ To increase the rate of success.
} 
\question 45.	Which of the following is true according to the text?\\
\fourch{ Personal search agents are indispensable to job-hunters.
}{ Some sites keep E-mailing job seekers to trace their demands.
}{ Personal search agents are also helpful to those already employed.
}{ Some agents stop sending information to people once they are employed.
}\end{questions}    \subsection{Text 2}
Over the past century, all kinds of unfairness and discrimination have been condemned or made illegal. But one insidious form continues to thrive: alphabetism. This, for those as yet unaware of such a disadvantage, refers to discrimination against those whose surnames begin with a letter in the lower half of the alphabet.
It has long been known that a taxi firm called AAAA cars has a big advantage over Zodiac cars when customers thumb through their phone directories. Less well known is the advantage that Adam Abbott has in life over Zoe Zysman. English names are fairly evenly spread between the halves of the alphabet. Yet a suspiciously large number of top people have surnames beginning with letters between A and K.
Thus the American president and vice-president have surnames starting with B and C respectively; and 26 of George Bush’s predecessors (including his father) had surnames in the first half of the alphabet against just 16 in the second half. Even more striking, six of the seven heads of government of the G7 rich countries are alphabetically advantaged (Berlusconi, Blair, Bush, Chirac, Chrétien and Koizumi). The world’s three top central bankers (Greenspan, Duisenberg and Hayami) are all close to the top of the alphabet, even if one of them really uses Japanese characters. As are the world’s five richest men (Gates, Buffett, Allen, Ellison and Albrecht).
Can this merely be coincidence? One theory, dreamt up in all the spare time enjoyed by the alphabetically disadvantaged, is that the rot sets in early. At the start of the first year in infant school, teachers seat pupils alphabetically from the front, to make it easier to remember their names. So short-sighted Zysman junior gets stuck in the back row, and is rarely asked the improving questions posed by those insensitive teachers. At the time the alphabetically disadvantaged may think they have had a lucky escape. Yet the result may be worse qualifications, because they get less individual attention, as well as less confidence in speaking publicly.
The humiliation continues. At university graduation ceremonies, the ABCs proudly get their awards first; by the time they reach the Zysmans most people are literally having a ZZZ. Shortlists for job interviews, election ballot papers, lists of conference speakers and attendees: all tend to be drawn up alphabetically, and their recipients lose interest as they plough through them.
\begin{questions} \sethlcolor{cyan} \question 46.	What does the author intend to illustrate with AAA A cars and Zodiac cars?\\
\fourch{ A kind of overlooked inequality.
}{ A type of conspicuous bias.
}{ A type of personal prejudice.
}{ A kind of brand discrimination.
} \question 47.	What can we infer from the first three paragraphs? \\
\fourch{ In both East and West, names are essential to success.
}{ The alphabet is to blame for the failure of Zoë Zysman.
}{ Customers often pay a lot of attention to companies’ names.
}{ Some form of discrimination is too subtle to recognize.
} \question 48.	The 4th paragraph suggests that \ltk{}.\\
\fourch{ questions are often put to the more intelligent students
}{ alphabetically disadvantaged students often escape from class
}{ teachers should pay attention to all of their students
}{ students should be seated according to their eyesight
} \question 49.	What does the author mean by “most people are literally having a ZZZ” (Lines 2-3, Paragraph 5)?\\
\fourch{ They are getting impatient.
}{ They are noisily dozing off.
}{ They are feeling humiliated.
}{ They are busy with word puzzles.
} \question 50.	Which of the following is true according to the text?\\
\fourch{ People with surnames beginning with N to Z are often ill-treated.
}{ VIPs in the Western world gain a great deal from alphabetism.
}{ The campaign to eliminate alphabetism still has a long way to go.
}{ Putting things alphabetically may lead to unintentional bias.
}\end{questions}    \subsection{Text 3}
When it comes to the slowing economy, Ellen Spero isn’t biting her nails just yet. But the 47-year-old manicurist isn’t cutting, filing or polishing as many nails as she’d like to, either. Most of her clients spend $12 to $50 weekly, but last month two longtime customers suddenly stopped showing up. Spero blames the softening economy. “I’m a good economic indicator,” she says. “I provide a service that people can do without when they’re concerned about saving some dollars.” So Spero is downscaling, shopping at middle-brow Dillard’s department store near her suburban Cleveland home, instead of Neiman Marcus. “I don’t know if other clients are going to abandon me, too.” she says.
Even before Alan Greenspan’s admission that America’s red-hot economy is cooling, lots of working folks had already seen signs of the slowdown themselves. From car dealerships to Gap outlets, sales have been lagging for months as shoppers temper their spending. For retailers, who last year took in 24 percent of their revenue between Thanksgiving and Christmas, the cautious approach is coming at a crucial time. Already, experts say, holiday sales are off 7 percent from last year’s pace. But don’t sound any alarms just yet. Consumers seem only mildly concerned, not panicked, and many say they remain optimistic about the economy’s long-term prospects, even as they do some modest belt-tightening.
Consumers say they’re not in despair because, despite the dreadful headlines, their own fortunes still feel pretty good. Home prices are holding steady in most regions. In Manhattan, “there’s a new gold rush happening in the $4 million to $10 million range, predominantly fed by Wall Street bonuses,” says broker Barbara Corcoran. In San Francisco, prices are still rising even as frenzied overbidding quiets. “Instead of 20 to 30 offers, now maybe you only get two or three,” says John Tealdi, a Bay Area real-estate broker. And most folks still feel pretty comfortable about their ability to find and keep a job.
Many folks see silver linings to this slowdown. Potential home buyers would cheer for lower interest rates. Employers wouldn’t mind a little fewer bubbles in the job market. Many consumers seem to have been influenced by stock-market swings, which investors now view as a necessary ingredient to a sustained boom. Diners might see an upside, too. Getting a table at Manhattan’s hot new Alain Ducasse restaurant used to be impossible. Not anymore. For that, Greenspan \& Co. may still be worth toasting.
\begin{questions} \sethlcolor{cyan} \question 52.	By “Ellen Spero isn’t biting her nails just yet” (Lines 1-2, Paragraph 1), the author means \ltk{}.\\
\fourch{ Spero can hardly maintain her business
}{ Spero is too much engaged in her work
}{ Spero has grown out of her bad habit
}{ Spero is not in a desperate situation
}  \question 52.	How do the public feel about the current economic situation?\\
\fourch{ Optimistic.
}{ Confused.
}{ Carefree.
}{ Panicked.
}  \question 53.	When mentioning “the \$4 million to \$10 million range” (Lines 3-4, Paragraph 3) the author is talking about \ltk{}.\\
\fourch{ gold market
}{ real estate
}{ stock exchange
}{ venture investment
}  \question 54.	Why can many people see “silver linings” to the economic slowdown?\\
\fourch{ They would benefit in certain ways.
}{ The stock market shows signs of recovery.
}{ Such a slowdown usually precedes a boom.
}{ The purchasing power would be enhanced.
} \question 55.	To which of the following is the author likely to agree?\\
\fourch{ A new boom, on the horizon.
}{ Tighten the belt, the single remedy.
}{ Caution all right, panic not.
}{ The more ventures, the more chances.
}
\end{questions}

\subsection{Text 4}
Americans today don’t place a very high value on intellect. Our heroes are athletes, entertainers, and entrepreneurs, not scholars. Even our schools are where we send our children to get a practical education -- not to pursue knowledge for the sake of knowledge. Symptoms of pervasive anti-intellectualism in our schools aren’t difficult to find.
“Schools have always been in a society where practical is more important than intellectual,” says education writer Diane Ravitch. “Schools could be a counterbalance.” Ravitch’s latest book, Left Back: A Century of Failed School Reforms, traces the roots of anti-intellectualism in our schools, concluding they are anything but a counterbalance to the American distaste for intellectual pursuits.
But they could and should be. Encouraging kids to reject the life of the mind leaves them vulnerable to exploitation and control. Without the ability to think critically, to defend their ideas and understand the ideas of others, they cannot fully participate in our democracy. Continuing along this path, says writer Earl Shorris, “We will become a second-rate country. We will have a less civil society.”
“Intellect is resented as a form of power or privilege,” writes historian and professor Richard Hofstadter in Anti-Intellectualism in American Life, a Pulitzer Prize winning book on the roots of anti-intellectualism in US politics, religion, and education. From the beginning of our history, says Hofstadter, our democratic and populist urges have driven us to reject anything that smells of elitism. Practicality, common sense, and native intelligence have been considered more noble qualities than anything you could learn from a book.
Ralph Waldo Emerson and other Transcendentalist philosophers thought schooling and rigorous book learning put unnatural restraints on children: “We are shut up in schools and college recitation rooms for 10 or 15 years and come out at last with a bellyful of words and do not know a thing.” Mark Twain’s Huckleberry Finn exemplified American anti-intellectualism. Its hero avoids being civilized -- going to school and learning to read -- so he can preserve his innate goodness.
Intellect, according to Hofstadter, is different from native intelligence, a quality we reluctantly admire. Intellect is the critical, creative, and contemplative side of the mind. Intelligence seeks to grasp, manipulate, re-order, and adjust, while intellect examines, ponders, wonders, theorizes, criticizes and imagines.
School remains a place where intellect is mistrusted. Hofstadter says our country’s educational system is in the grips of people who “joyfully and militantly proclaim their hostility to intellect and their eagerness to identify with children who show the least intellectual promise.”
\begin{questions} \sethlcolor{cyan} \question  56.	What do American parents expect their children to acquire in school?\\
\fourch{ The habit of thinking independently.
}{ Profound knowledge of the world.
}{ Practical abilities for future career.
}{ The confidence in intellectual pursuits.
} \question 57.	We can learn from the text that Americans have a history of \ltk{}.\\
\fourch{ undervaluing intellect
}{ favoring intellectualism
}{ supporting school reform
}{ suppressing native intelligence
} \question 58.	The views of Ravitch and Emerson on schooling are \ltk{}.\\
\fourch{ identical
}{ similar
}{ complementary
}{ opposite
} \question 59.	Emerson, according to the text, is probably \ltk{}.\\
\fourch{ a pioneer of education reform
}{ an opponent of intellectualism
}{ a scholar in favor of intellect
}{ an advocate of regular schooling
} \question 60.	What does the author think of intellect?\\
\fourch{ It is second to intelligence.
}{ It evolves from common sense.
}{ It is to be pursued.
}{ It underlies power.
}\end{questions}